Pop-up cycleways provide a peak into post COVID-19 transport futures

### 2020-05-11 conversation.Rmd
Add tweet

---
title: "Pop-up cycleways: a peak into post COVID-19 transport futures"
---

@@

Many pop-up interventions have already been documented internationally and in the UK and there is much to learn much from these experiences already.
There are three broad categories of pop-up interventions...
Geographically, cities with pop-up infrastructure range from [Milan] to [Martin Luther King Jr Drive in Philadelphia](https://www.theguardian.com/world/2020/apr/11/world-cities-turn-their-streets-over-to-walkers-and-cyclists ""), [Auckland](https://www.roadtraffic-technology.com/news/nz-govt-extra-wide-footpaths/) to [Mexico City](https://bicitekas.org/sites/default/files/public/manuales/propuesta_ciclovias_temporales_cdmxvfinal.pdf). Never has there been such a need for affordable, healthy and socially distanced transport that does not create the fumes that [emerging evidence] links to coronavirus susceptibility.

>>>>

---
title: "Pop-up cycleways provide a peak into post COVID-19 transport futures"
---

@@

Many pop-up interventions have already been documented internationally and in the UK and there is much to learn much from these experiences already.
Geographically, cities with pop-up infrastructure range from [Milan] to [Martin Luther King Jr Drive in Philadelphia](https://www.theguardian.com/world/2020/apr/11/world-cities-turn-their-streets-over-to-walkers-and-cyclists ""), [Auckland](https://www.roadtraffic-technology.com/news/nz-govt-extra-wide-footpaths/) to [Mexico City](https://bicitekas.org/sites/default/files/public/manuales/propuesta_ciclovias_temporales_cdmxvfinal.pdf). Never has there been such a need for affordable, healthy and socially distanced transport that does not create the fumes that [emerging evidence] links to coronavirus susceptibility.

These interventions can be classified into three broad groups, as outlined in a [paper](add link) that we have written outlining methods for prioritising pop-up active transport infrastructure.

First...

An example of the first type of intervention is illustrated in the image below, from Salford, Manchester

[![](https://pbs.twimg.com/media/EXZ1t2EXgAELrdO?format=jpg&name=large)](https://twitter.com/CatrionaSwanson/status/1258322956595453952)

<tweet url="https://twitter.com/CatrionaSwanson/status/1258322956595453952" />

Second...
Third...
